BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-17 tex/2-related-work.tex
Related work started

\section{Related work}
2-related-work.tex

Web Object Identification for Web Automation and Meta-Search,
\\
http://www.dbai.tuwien.ac.at/proj/ta\\
mcrow/download/Kordomatis2013WIMS.pdf

Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
\\
https://github.com/OlivierBlanvillai\\
n/blogforever-crawler-publication/raw\\
/master/papers/bncod\_published.pdf

Web Data Extraction, Applications and Techniques: A Survey,
\\
http://www.emilio.ferrara.name/wp-co\\
ntent/uploads/2011/07/survey-csur.pdf

Archiving Data Objects using Web Feeds,
\\
http://hal.archives-ouvertes.fr/docs\\
/00/53/79/62/PDF/iwawienna.pdf

Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
\\
http://pierre.senellart.com/publicat\\
ions/faheem2013intelligent.pdf

Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
\\
http://www2013.org/companion/p73.pdf\\

OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
\\
http://www.vldb.org/pvldb/vol4/p1016\\
-furche.pdf

>>>>

\section{Related work}

- Web crawlers

we merged the crawling phase with the contente extraction which removed the need to store all web pages material and leads to a lighter process as we directly send things to the db

- Blog crawlers
focused on blog detection and content analysis such as political mouvement or popular personalities.

- Wrapper generation
these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.

% Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
% \comment{Mention Internet Archive here and maybe another generic web archiving project}

% A fraction of web archiving studies and projects focus on the specific problem of blog harvesting and archiving.
% They focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
% Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
% (In this section we review some studies and projects that introduce and describe such techniques.)

% Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
% Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
% Given their format, web feeds constitute an excellent source for blog archiving.
% They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
% More advanced methods and techniques have to be employed in order to achieve quality blog archiving.

% Here mention projects that use web feeds for discovery and compare them to ours.
% \begin{itemize}
%   \item ( Zero-cost Labelling with Web Feeds for Weblog Data Extraction - http://www2013.org/companion/p73.pdf).
%   \item ( Self-supervised Automated Wrapper Generation for Weblog Data Extraction - https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf).
%   \item ( Archiving Data Objects using Web Feeds - http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf).
% \end{itemize}
% Some of these should also be in the comparison for extraction methods.

% Here mention projects that use other techniques for discovery and compare them to ours.
% \begin{itemize}
%   \item ???
% \end{itemize}

% Here mention projects that use various techniques for extraction and compare them to ours.
% \begin{itemize}
%   \item ( Web Object Identification for Web Automation and Meta-Search - http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf).
%   \item ( OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications - http://www.vldb.org/pvldb/vol4/p1016-furche.pdf).
%   \item ( Intelligent and Adaptive Crawling of Web Applications for Web Archiving - http://pierre.senellart.com/publications/faheem2013intelligent.pdf).
%   \item ( Web Data Extraction, Applications and Techniques: A Survey - http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf).
% \end{itemize}

% Here mention that there is no comparison for the JavaScript rendering as there are no similar projects.
% \begin{itemize}
%   \item ???
% \end{itemize}

### 2014-01-17 tex/4-techniques.tex
Into on RSS almost done, some issues to compile w latexmk
Related work started

% Motivation
In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2014} comment hosting services. For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.

@@

>>>>

% Motivation
In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services. For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.

@@

\TODO{Write this properly...}
One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material. Instead, the content of interest is computed "on the fly", and directly saved into the back-end system. This propriety ...
